Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-26 autovi_paper.qmd
comment
I'd refer to documentation rather than the website here -- it should be in both places, so don't confine it to the web. If it's only on the website, we probably should add it to the full package documentation.

This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis.

@@

The modules for VSS prediction and $p$-value computation are predefined and cannot be overridden, although users can interact with them directly through function arguments. Similarly, the image reading and resizing module is fixed but will adapt to different Keras models by checking their input shapes. The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs. These modules are discussed in detail on the software's website. <!-- in the following sections.-->
<!-- FIXME: ET: which website? >
<!--
### Initialization

>>>>

This visual summary provides an intuitive way to assess the model's fit and potential violations, allowing users to quickly grasp the results of the automated analysis. XXX It might be a good idea to include a basic message explaining the plot and how it's used when it is generated, because a lot of non-statisticians aren't going to be used to interpreting these plots XXX

@@

The modules for VSS prediction and $p$-value computation are predefined and cannot be overridden, although users can interact with them directly through function arguments. Similarly, the image reading and resizing module is fixed but will adapt to different Keras models by checking their input shapes. The remaining seven modules are designed to be overridable, enabling users to tailor the infrastructure to their specific needs. These modules are discussed in detail in the package documentation. <!-- in the following sections.-->
<!-- FIXME: ET: which website? >
<!--
### Initialization
